---
title: "Exploratory Analyses"
author: "Jaime Chen"
date: "2025-03-12"
output: html_document
---

```{r}
library(ggplot2)
```


# d' (training and learning) by age group (5-, 6-, 7-, 8-yos, and adults)

```{r}
age_list = as.character(kid_participant_info$age_group)
age_cont = kid_participant_info$age_mos / 12

subj_test_dprime_avg_training <- subj_test_accuracy_all %>% 
  group_by(participant, sample_group) %>%
  summarize(dprime_t = mean(dprime_training)) %>% ungroup()

subj_test_dprime_avg_label <- subj_test_accuracy_all %>% 
  group_by(participant, sample_group) %>% 
  summarize(dprime_l = mean(dprime_label)) %>% ungroup()

subj_test_dprime_avg <- subj_test_dprime_avg_training %>% mutate(dprime_l = subj_test_dprime_avg_label$dprime_l)

subj_test_dprime_avg_children <- subj_test_dprime_avg %>%
  filter(sample_group == "children") %>% 
  mutate(age_group = age_list) %>% 
  mutate(age = age_cont)
subj_test_dprime_avg_adult <- subj_test_dprime_avg %>% 
  filter(sample_group == "adults") %>% 
  mutate(age_group = "adult") %>% 
  mutate(age = NA)
subj_test_dprime_avg_clean <- rbind(subj_test_dprime_avg_children, subj_test_dprime_avg_adult)


# plotting d' by age group

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_t, x=age_group)) + geom_violin(draw_quantiles = c(0.5), aes(color=age_group, alpha = 0.1)) + geom_jitter(aes(color = age_group, stroke = 0), size = 2) + theme(legend.position="none")

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_l, x=age_group)) + geom_violin(draw_quantiles = c(0.5), aes(color=age_group, alpha = 0.1)) + geom_jitter(aes(color = age_group, stroke = 0), size = 2) + theme(legend.position="none")

# plotting d' by continuous age

lm_t <- lm(dprime_t ~ age, data = subj_test_dprime_avg_clean)
lm_l <- lm(dprime_l ~ age, data = subj_test_dprime_avg_clean)

summary(lm_t)
summary(lm_l)

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_t, x=age)) + geom_point() + geom_smooth(method='lm')
subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_l, x=age)) + geom_point() + geom_smooth(method='lm')


```


# Sampling-Test Interaction
## exploratory choices --> broader extensions?
## adult vs children
### will probably see that exploratory predicts broader extension with adults
### will probably not see this predictor with children --> not effectively using sampling yet?
##### --> age effect?

```{r}
exploratory <- combined_sampling_data %>% 
  select(sample_group, participant, trial_counter, is_exploratory) %>%
  sort_by(combined_sampling_data$sample_group, combined_sampling_data$participant) %>%
  mutate(is_exploratory = as.character(is_exploratory)) %>% mutate(is_exploratory_yn = case_when(
    is_exploratory == 1 ~ "explored",
    is_exploratory == 0 ~ "did not explore",
    TRUE ~ is_exploratory
  ))

fa_rate <- subj_test_accuracy_all %>% 
  ungroup() %>% 
  select(sample_group, participant, false_alarm_rate_training_adj, false_alarm_rate_label_adj) %>%
  sort_by(subj_test_accuracy_all$sample_group, subj_test_accuracy_all$participant) %>%
  select(false_alarm_rate_training_adj, false_alarm_rate_label_adj)

choices <- subj_test_accuracy %>% ungroup() %>% select(total_choices, ground_truth_correct_choices, ground_truth_incorrect_choices, training_consistent_choices, training_inconsistent_choices) %>% mutate(training_inconsistent_prop = training_inconsistent_choices/total_choices)

exploratory_interact <- cbind(exploratory, fa_rate, choices)


# adjusted FA rate based on exploration during sampling for each round

exploratory_interact %>% ggplot(aes(x = is_exploratory_yn, y = false_alarm_rate_training_adj)) + geom_violin()
exploratory_interact %>% ggplot(aes(x = is_exploratory_yn, y = false_alarm_rate_label_adj)) + geom_violin()


# total choices made based off of explored/didn't explore during sampling for each round

exploratory_interact %>% ggplot(aes(total_choices, fill = is_exploratory_yn)) + 
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  geom_density(adjust = 5, alpha = 0.3, linewidth = 0) +
  facet_wrap(~ is_exploratory_yn) + 
  scale_x_continuous(breaks=seq(0,12,1))+ 
  theme(legend.position="none")


# proportion of training inconsistent choices based on exploration

class(exploratory_interact$training_inconsistent_prop)

exploratory_interact %>% ggplot(aes(x = is_exploratory_yn, y = training_inconsistent_prop, fill = is_exploratory_yn)) + 
  geom_violin() + 
  stat_summary(fun = "mean", geom = "crossbar", size = 0.3, width = 0.4) + 
  theme(legend.position="none")

```




# hit vs FA


# did participants limit test choices based on best extension confirmed/discovered by sampling (match b/w samp and test)
## adult vs children
### probably yes with adults
### probably no with kids --> age effect?


```{r}

```

