---
title: "Exploratory Analyses"
author: "Jaime Chen"
date: "2025-03-12"
output: html_document
---

```{r}
library(ggplot2)
```


# d' (training and learning) by age group (5-, 6-, 7-, 8-yos, and adults)

```{r}
age_list = as.character(kid_participant_info$age_group)
age_cont = kid_participant_info$age_mos / 12

subj_test_dprime_avg_training <- subj_test_accuracy_all %>% 
  group_by(participant, sample_group) %>%
  summarize(dprime_t = mean(dprime_training)) %>% ungroup()

subj_test_dprime_avg_label <- subj_test_accuracy_all %>% 
  group_by(participant, sample_group) %>% 
  summarize(dprime_l = mean(dprime_label)) %>% ungroup()

subj_test_dprime_avg <- subj_test_dprime_avg_training %>% mutate(dprime_l = subj_test_dprime_avg_label$dprime_l)

subj_test_dprime_avg_children <- subj_test_dprime_avg %>%
  filter(sample_group == "children") %>% 
  mutate(age_group = age_list) %>% 
  mutate(age = age_cont)
subj_test_dprime_avg_adult <- subj_test_dprime_avg %>% 
  filter(sample_group == "adults") %>% 
  mutate(age_group = "adult") %>% 
  mutate(age = NA)
subj_test_dprime_avg_clean <- rbind(subj_test_dprime_avg_children, subj_test_dprime_avg_adult)


# plotting d' by age group

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_t, x=age_group)) + geom_violin(draw_quantiles = c(0.5), aes(color=age_group, alpha = 0.1)) + geom_jitter(aes(color = age_group, stroke = 0), size = 2) + theme(legend.position="none")

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_l, x=age_group)) + geom_violin(draw_quantiles = c(0.5), aes(color=age_group, alpha = 0.1)) + geom_jitter(aes(color = age_group, stroke = 0), size = 2) + theme(legend.position="none")

# plotting d' by continuous age

lm_t <- lm(dprime_t ~ age, data = subj_test_dprime_avg_clean)
lm_l <- lm(dprime_l ~ age, data = subj_test_dprime_avg_clean)

summary(lm_t)
summary(lm_l)

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_t, x=age)) + geom_point() + geom_smooth(method='lm')
subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_l, x=age)) + geom_point() + geom_smooth(method='lm')


```


# Sampling-Test Interaction
## Exploration-Test
### Do exploratory choices lead to broader extensions in children and adults?

```{r}
exploratory <- combined_sampling_data %>% 
  select(sample_group, participant, trial_counter, is_exploratory) %>%
  sort_by(combined_sampling_data$sample_group, combined_sampling_data$participant) %>%
  mutate(is_exploratory = as.character(is_exploratory)) %>% mutate(is_exploratory_yn = case_when(
    is_exploratory == 1 ~ "explored",
    is_exploratory == 0 ~ "did not explore",
    TRUE ~ is_exploratory
  ))

fa_rate <- subj_test_accuracy_all %>% 
  ungroup() %>% 
  select(sample_group, participant, false_alarm_rate_training_adj, false_alarm_rate_label_adj) %>%
  sort_by(subj_test_accuracy_all$sample_group, subj_test_accuracy_all$participant) %>%
  select(false_alarm_rate_training_adj, false_alarm_rate_label_adj)

choices <- subj_test_accuracy %>% ungroup() %>% select(total_choices, ground_truth_correct_choices, ground_truth_incorrect_choices, training_consistent_choices, training_inconsistent_choices) %>% mutate(training_inconsistent_prop = training_inconsistent_choices/total_choices)

exploratory_interact <- cbind(exploratory, fa_rate, choices)


# adjusted FA rate based on exploration during sampling for each round

exploratory_interact %>% ggplot(aes(x = is_exploratory_yn, y = false_alarm_rate_training_adj)) + geom_violin() + geom_jitter(aes(color = is_exploratory_yn), size = 0.75, alpha = 0.5) + facet_wrap(~ sample_group) + theme(legend.position="none")

exploratory_interact %>% ggplot(aes(x = is_exploratory_yn, y = false_alarm_rate_label_adj)) + geom_violin() + facet_wrap(~ sample_group)


# total choices made based off of explored/didn't explore during sampling for each round

exploratory_interact %>% ggplot(aes(total_choices, fill = is_exploratory_yn)) + 
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  geom_density(bw = 0.75, alpha = 0.3, linewidth = 0) +
  facet_grid(sample_group ~ is_exploratory_yn) + 
  scale_x_continuous(breaks=seq(0,12,1))+ 
  theme(legend.position="none")


# proportion of training inconsistent choices based on exploration

class(exploratory_interact$training_inconsistent_prop)

exploratory_interact %>% ggplot(aes(x = is_exploratory_yn, y = training_inconsistent_prop, fill = is_exploratory_yn)) + 
  geom_violin() + 
  stat_summary(fun = "mean", geom = "crossbar", size = 0.3, width = 0.4) + 
  theme(legend.position="none") + facet_wrap(~ sample_group)

```





## Sampling Consistency of Test Choices
### Did participants limit test choices based on best extension confirmed/discovered by sampling and training (match b/w samp and test)?

#### Children

```{r}
kid_sampling_samptestint <- kid_sampling_data %>% select(participant, age_group, age_years, age_mos, exclude_participant, trial_counter, round, number_training_images, current_category_kind, current_category_training_level, current_hypernym_category_kind, sampled_image, sampled_imagelabel, sampled_category_kind, sampled_category_level, sampling_choice_type, sampled_label) %>% group_by(participant, trial_counter) %>% 
  mutate(current_category_training_level = case_when(
    number_training_images == 1 ~ "sub",
    number_training_images == 3 & current_category_training_level == "narrow" ~ "sub",
    number_training_images == 3 & current_category_training_level == "intermediate" ~ "bas",
    number_training_images == 3 & current_category_training_level == "broad" ~ "sup",
    TRUE ~ current_category_training_level
  ))

kid_sampling_samptestint <- kid_sampling_samptestint %>% 
  mutate(sampling_consistent_cat = case_when(
    current_category_kind == sampled_category_kind ~ substr(current_category_kind, start=1, stop=3),
    current_category_kind != sampled_category_kind & "not" == substr(sampled_label, start=1, stop=3) ~ substr(current_category_kind, start=1, stop=3),
    current_category_kind != sampled_category_kind & "not" != substr(sampled_label, start=1, stop=3) ~ paste(substr(current_category_kind, start=1, stop=3), substr(sampled_category_kind, start=1, stop=3)),
    TRUE ~ current_category_kind
  )) %>% 
  mutate(current_category_training_level_num = case_when(
    current_category_training_level == "sub" ~ 1,
    current_category_training_level == "bas" ~ 2,
    current_category_training_level == "sup" ~ 3,
    TRUE ~ 0
  )) %>% 
  mutate(sampled_category_level_num = case_when(
    sampled_category_level == "sub" ~ 1,
    sampled_category_level == "bas" ~ 2,
    current_category_kind == sampled_category_kind & sampled_category_level == "sup" ~ 3,
    current_category_kind != sampled_category_kind ~ 4,
    TRUE ~ 0
  )) %>% 
  mutate(sampling_consistent_level = case_when(
    current_category_kind != sampled_category_kind & "not" != substr(sampled_label, start=1, stop=3) ~ "hyp",
    "not" != substr(sampled_label, start=1, stop=3) & sampled_category_level_num >= current_category_training_level_num ~ sampled_category_level,
    "not" != substr(sampled_label, start=1, stop=3) & sampled_category_level_num < current_category_training_level_num ~ current_category_training_level,
    "not" == substr(sampled_label, start=1, stop=3) ~ current_category_training_level,
    TRUE ~ NA
  ))

kid_test_samptestint <- kid_test_array_options_clean %>% select(participant, trial_counter, round, test_image, is_chosen)

kid_samptestint <- merge(kid_test_samptestint, kid_sampling_samptestint)


hyp_consistent = c("sub", "bas", "sup", "hyp")
sup_consistent = c("sub", "bas", "sup")
bas_consistent = c("sub", "bas")
sub_consistent = c("sub")


# how many sampling+training consistent choices they made (e.g, sampling_consistent is 1 and is_chosen is 1)
# how many sampling+training inconsistent choices they made (e.g, sampling_consistent is 0 but is_chosen is 1)
# how many sampling+training consistent choices they missed (e.g, sampling_consistent is 1 but is_chosen is 0)

kid_samptestint <- kid_samptestint %>% rowwise() %>% 
  mutate(test_image_level = case_when(
    grepl("sub", test_image) ~ "sub",
    grepl("bas", test_image) ~ "bas",
    grepl("sup", test_image) ~ "sup",
    TRUE ~ test_image
  )) %>%
  mutate(test_image_cat = case_when(
    grepl((substr(current_hypernym_category_kind, start=1, stop=3)), test_image) ~ "out_hyp",
    grepl((substr(current_category_kind, start=1, stop=3)), test_image) ~ "in",
    .default = "out"
  ))

kid_samptestint <- kid_samptestint %>%
  mutate(sampling_consistent = case_when(
    sampling_consistent_level == "sub" & test_image_cat == "in" & test_image_level == "sub" ~ 1,
    sampling_consistent_level == "bas" & test_image_cat == "in" & test_image_level == "bas" ~ 1,
    sampling_consistent_level == "bas" & test_image_level == "sub" ~ 1,
    sampling_consistent_level == "sup" & test_image_cat == "in" ~ 1,
    sampling_consistent_level == "hyp" & test_image_cat == "in" ~ 1,
    sampling_consistent_level == "hyp" & test_image_cat == "out_hyp" ~ 1,
    .default = 0
  ))

kid_sample_choice_consistency <- kid_samptestint %>% ungroup() %>% group_by(participant, trial_counter) %>% select(participant, age_group, age_years, age_mos, trial_counter, round, number_training_images, current_category_training_level, sampling_consistent_level, is_chosen, sampling_consistent, current_category_training_level_num, sampled_category_level_num) %>% 
  mutate(choice_type = case_when(
    is_chosen == 1 & sampling_consistent == 1 ~ "hit",
    is_chosen == 1 & sampling_consistent == 0 ~ "false_alarm",
    is_chosen == 0 & sampling_consistent == 1 ~ "miss",
    is_chosen == 0 ~ "correct_reject",
    .default = NA
  ))

kid_choice_type_count <- kid_sample_choice_consistency %>% 
  ungroup() %>% 
  group_by(participant) %>% 
  count(choice_type)

kid_choice_type_count %>% ggplot(aes(x = choice_type, y = n)) + geom_violin()

kid_choice_type_rate <- kid_choice_type_count %>% 
  pivot_wider(names_from = choice_type, values_from = n)

kid_choice_type_rate[is.na(kid_choice_type_rate)] <- 0

kid_participant_ages <- kid_sampling_data %>% select(participant, age_group, age_years, age_mos) %>% unique() %>% mutate(group = case_when(
    TRUE ~ "1_child"
  ))

kid_choice_type_rate <- kid_choice_type_rate %>% mutate(hit_rate = hit/(hit+miss)) %>% mutate(fa_rate = false_alarm/(false_alarm+correct_reject)) %>% ungroup() %>% mutate(miss_rate = miss/(hit+miss)) %>% merge(kid_participant_ages)

kid_choice_type_rate %>% ggplot(aes(x=age_years, y=hit_rate)) + geom_point()
kid_choice_type_rate %>% ggplot(aes(x=age_years, y=fa_rate)) + geom_point()
kid_choice_type_rate %>% ggplot(aes(x=age_years, y=miss_rate)) + geom_point()

```

#### Adults

```{r}
adult_hypernym_data <- adult_d %>% select(participant, current_category_kind, current_hypernym_category_kind) %>% unique() %>% na.omit()

adult_sampling_data <- merge(adult_sampling_data, adult_hypernym_data)

adult_sampling_samptestint <- adult_sampling_data %>% select(participant, exclude_participant, trial_counter, round, number_training_images, current_category_kind, current_category_training_level, current_hypernym_category_kind, sampled_image, sampled_imagelabel, sampled_category_kind, sampled_category_level, sampling_choice_type, sampled_label) %>% group_by(participant, trial_counter) %>% 
  mutate(current_category_training_level = case_when(
    number_training_images == 1 ~ "sub",
    number_training_images == 3 & current_category_training_level == "narrow" ~ "sub",
    number_training_images == 3 & current_category_training_level == "intermediate" ~ "bas",
    number_training_images == 3 & current_category_training_level == "broad" ~ "sup",
    TRUE ~ current_category_training_level
  ))

adult_sampling_samptestint <- adult_sampling_samptestint %>% 
  mutate(sampling_consistent_cat = case_when(
    current_category_kind == sampled_category_kind ~ substr(current_category_kind, start=1, stop=3),
    current_category_kind != sampled_category_kind & "not" == substr(sampled_label, start=1, stop=3) ~ substr(current_category_kind, start=1, stop=3),
    current_category_kind != sampled_category_kind & "not" != substr(sampled_label, start=1, stop=3) ~ paste(substr(current_category_kind, start=1, stop=3), substr(sampled_category_kind, start=1, stop=3)),
    TRUE ~ current_category_kind
  )) %>% 
  mutate(current_category_training_level_num = case_when(
    current_category_training_level == "sub" ~ 1,
    current_category_training_level == "bas" ~ 2,
    current_category_training_level == "sup" ~ 3,
    TRUE ~ 0
  )) %>% 
  mutate(sampled_category_level_num = case_when(
    sampled_category_level == "sub" ~ 1,
    sampled_category_level == "bas" ~ 2,
    current_category_kind == sampled_category_kind & sampled_category_level == "sup" ~ 3,
    current_category_kind != sampled_category_kind ~ 4,
    TRUE ~ 0
  )) %>% 
  mutate(sampling_consistent_level = case_when(
    current_category_kind != sampled_category_kind & "not" != substr(sampled_label, start=1, stop=3) ~ "hyp",
    "not" != substr(sampled_label, start=1, stop=3) & sampled_category_level_num >= current_category_training_level_num ~ sampled_category_level,
    "not" != substr(sampled_label, start=1, stop=3) & sampled_category_level_num < current_category_training_level_num ~ current_category_training_level,
    "not" == substr(sampled_label, start=1, stop=3) ~ current_category_training_level,
    TRUE ~ NA
  ))
# what about when sampling gives "not a ___" but they sampled 2 or 3 levels up (e.g., sub training, sup/hyp sampling)

adult_test_samptestint <- adult_test_array_options_clean %>% select(participant, trial_index, round, test_image, is_chosen) %>% mutate(trial_counter = (trial_index-1)/7) %>% select(participant, trial_counter, round, test_image, is_chosen)

adult_samptestint <- merge(adult_test_samptestint, adult_sampling_samptestint)

hyp_consistent = c("sub", "bas", "sup", "hyp")
sup_consistent = c("sub", "bas", "sup")
bas_consistent = c("sub", "bas")
sub_consistent = c("sub")

# how many sampling+training consistent choices they made (e.g, sampling_consistent is 1 and is_chosen is 1)
# how many sampling+training inconsistent choices they made (e.g, sampling_consistent is 0 but is_chosen is 1)
# how many sampling+training consistent choices they missed (e.g, sampling_consistent is 1 but is_chosen is 0)

adult_samptestint <- adult_samptestint %>% rowwise() %>% 
  mutate(test_image_level = case_when(
    grepl("sub", test_image) ~ "sub",
    grepl("bas", test_image) ~ "bas",
    grepl("sup", test_image) ~ "sup",
    TRUE ~ test_image
  )) %>%
  mutate(test_image_cat = case_when(
    grepl((substr(current_hypernym_category_kind, start=1, stop=3)), test_image) ~ "out_hyp",
    grepl((substr(current_category_kind, start=1, stop=3)), test_image) ~ "in",
    .default = "out"
  ))

adult_samptestint <- adult_samptestint %>%
  mutate(sampling_consistent = case_when(
    sampling_consistent_level == "sub" & test_image_cat == "in" & test_image_level == "sub" ~ 1,
    sampling_consistent_level == "bas" & test_image_cat == "in" & test_image_level == "bas" ~ 1,
    sampling_consistent_level == "bas" & test_image_level == "sub" ~ 1,
    sampling_consistent_level == "sup" & test_image_cat == "in" ~ 1,
    sampling_consistent_level == "hyp" & test_image_cat == "in" ~ 1,
    sampling_consistent_level == "hyp" & test_image_cat == "out_hyp" ~ 1,
    .default = 0
  ))


adult_sample_choice_consistency <- adult_samptestint %>% ungroup() %>% group_by(participant, trial_counter) %>% select(participant, trial_counter, round, number_training_images, current_category_training_level, sampling_consistent_level, is_chosen, sampling_consistent, current_category_training_level_num, sampled_category_level_num) %>% 
  mutate(choice_type = case_when(
    is_chosen == 1 & sampling_consistent == 1 ~ "hit",
    is_chosen == 1 & sampling_consistent == 0 ~ "false_alarm",
    is_chosen == 0 & sampling_consistent == 1 ~ "miss",
    is_chosen == 0 ~ "correct_reject",
    .default = NA
  ))

adult_choice_type_count <- adult_sample_choice_consistency %>% 
  ungroup() %>% 
  group_by(participant) %>% 
  count(choice_type)

adult_choice_type_count %>% ggplot(aes(x = choice_type, y = n)) + geom_violin()

adult_choice_type_rate <- adult_choice_type_count %>% 
  pivot_wider(names_from = choice_type, values_from = n)

adult_choice_type_rate[is.na(adult_choice_type_rate)] <- 0

adult_participant_ages <- adult_sampling_data %>% select(participant) %>% unique() %>% 
  mutate(age_years = case_when(
    TRUE ~ 25
  )) %>% 
  mutate(group = case_when(
    TRUE ~ "2_adult"
  ))

adult_choice_type_rate <- adult_choice_type_rate %>% mutate(hit_rate = hit/(hit+miss)) %>% mutate(fa_rate = false_alarm/(false_alarm+correct_reject)) %>% ungroup() %>% mutate(miss_rate = miss/(hit+miss)) %>% merge(adult_participant_ages)
```

#### Plotting Children and Adults together

```{r}
kid_choice_type_rate_2 <- kid_choice_type_rate %>% select(-age_group, -age_mos)

samptestint_choice_type_rate <- rbind(adult_choice_type_rate, kid_choice_type_rate_2)

plot1 <- samptestint_choice_type_rate %>% filter(group == "1_child") %>% ggplot(aes(x = age_years, y = hit_rate)) + geom_point() + scale_y_continuous(limits=c(-0.01, 1.01)) + geom_smooth(method = "lm")

plot2 <- samptestint_choice_type_rate %>% filter(group == "2_adult") %>% ggplot(aes(x = group, y = hit_rate)) + geom_jitter() + scale_y_continuous(limits=c(-0.01, 1.01))

plot3 <- samptestint_choice_type_rate %>% filter(group == "1_child") %>% ggplot(aes(x = age_years, y = fa_rate)) + geom_point() + scale_y_continuous(limits=c(-0.01, 1.01)) + geom_smooth(method = "lm")

plot4 <- samptestint_choice_type_rate %>% filter(group == "2_adult") %>% ggplot(aes(x = group, y = fa_rate)) + geom_jitter() + scale_y_continuous(limits=c(-0.01, 1.01))

plot5 <- samptestint_choice_type_rate %>% filter(group == "1_child") %>% ggplot(aes(x = age_years, y = miss_rate)) + geom_point() + scale_y_continuous(limits=c(-0.01, 1.01)) + geom_smooth(method = "lm")

plot6 <- samptestint_choice_type_rate %>% filter(group == "2_adult") %>% ggplot(aes(x = group, y = miss_rate)) + geom_jitter() + scale_y_continuous(limits=c(-0.01, 1.01))

(plot1+plot2)
(plot3+plot4)
(plot5+plot6)
```

## Exploration Consistent Test Choices?
### Did exploration (and associated sampling feedback) actually have an effect on how participants extended the novel word? 

#### Separating participants by explored/didn't explore 

```{r}
exp_adult_samptestint <- adult_samptestint %>% mutate(explored_yn = case_when(
  sampled_category_level_num > current_category_training_level_num ~ "explored",
  sampled_category_level_num <= current_category_training_level_num ~ "did not explore",
  TRUE ~ NA
)) %>% 
  mutate(samp_feedback_type = case_when(
    current_category_training_level == sampling_consistent_level & sampling_choice_type == "explore" ~ "negative",
    current_category_training_level != sampling_consistent_level & sampling_choice_type == "explore" ~ "positive",
    sampling_choice_type == "confirm" ~ "confirming",
    TRUE ~ NA
  )) %>% 
  ungroup() %>% group_by(participant, trial_counter)

exp_kid_samptestint <- kid_samptestint %>% mutate(explored_yn = case_when(
  sampled_category_level_num > current_category_training_level_num ~ "explored",
  sampled_category_level_num <= current_category_training_level_num ~ "did not explore",
  TRUE ~ NA
)) %>% 
  mutate(samp_feedback_type = case_when(
    current_category_training_level == sampling_consistent_level & sampling_choice_type == "explore" ~ "negative",
    current_category_training_level != sampling_consistent_level & sampling_choice_type == "explore" ~ "positive",
    sampling_choice_type == "confirm" ~ "confirming",
    TRUE ~ NA
  )) %>% 
  ungroup() %>% group_by(participant, trial_counter)

exp_adult_samptestint_summarized <- exp_adult_samptestint %>% filter(is_chosen == 1) %>% summarize(prop_sampinconsistent_choices = sum(is_chosen - sampling_consistent)/sum(is_chosen), explored_yn, samp_feedback_type) %>% unique() %>% mutate(samp_group = "adult")

exp_kid_samptestint_summarized <- exp_kid_samptestint %>% filter(is_chosen == 1) %>% summarize(prop_sampinconsistent_choices = sum(is_chosen - sampling_consistent)/sum(is_chosen), explored_yn, samp_feedback_type) %>% unique() %>% mutate(samp_group = "child")

exp_samptestint_summarized <- rbind(exp_adult_samptestint_summarized, exp_kid_samptestint_summarized)

exp_samptestint_summarized %>% ggplot(aes(x = samp_group, y = prop_sampinconsistent_choices, color = samp_group)) + geom_violin() + geom_jitter(alpha = 0.2) + facet_grid(explored_yn~samp_feedback_type)
```



# Play with participant-provided hypotheses