---
title: "Exploratory Analyses"
author: "Jaime Chen"
date: "2025-03-12"
output: html_document
---

# d' (training and learning) by age group (5-, 6-, 7-, 8-yos, and adults)

```{r}
age_list = as.character(kid_participant_info$age_group)

subj_test_dprime_avg_training <- subj_test_accuracy_all %>% 
  group_by(participant, sample_group) %>%
  summarize(dprime_t = mean(dprime_training)) %>% ungroup()

subj_test_dprime_avg_label <- subj_test_accuracy_all %>% 
  group_by(participant, sample_group) %>% 
  summarize(dprime_l = mean(dprime_label)) %>% ungroup()

subj_test_dprime_avg <- subj_test_dprime_avg_training %>% mutate(dprime_l = subj_test_dprime_avg_label$dprime_l)

subj_test_dprime_avg_children <- subj_test_dprime_avg %>%
  filter(sample_group == "children") %>% 
  mutate(age_group = age_list)
subj_test_dprime_avg_adult <- subj_test_dprime_avg %>% 
  filter(sample_group == "adults") %>% 
  mutate(age_group = "adult")
subj_test_dprime_avg_clean <- rbind(subj_test_dprime_avg_children, subj_test_dprime_avg_adult)

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_t, x=age_group)) + geom_violin(draw_quantiles = c(0.5), aes(color=age_group, alpha = 0.1)) + geom_jitter(aes(color = age_group, stroke = 0), size = 2)

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_l, x=age_group)) + geom_violin(draw_quantiles = c(0.5), aes(color=age_group, alpha = 0.1)) + geom_jitter(aes(color = age_group, stroke = 0), size = 2)
```


# Sampling-Test Interaction
## exploratory choices --> broader extensions?
## adult vs children
### will probably see that exploratory predicts broader extension with adults
### will probably not see this predictor with children --> not effectively using sampling yet?
##### --> age effect?


# correctness by exploratory?

# hit vs FA


# did participants limit test choices based on best extension confirmed/discovered by sampling (match b/w samp and test)
## adult vs children
### probably yes with adults
### probably no with kids --> age effect?


```{r}
# combined_sampling_data %>% group_by(sample_group) %>% select(is_exploratory)
# use subj_test_accuracy_all for test choices
```

