---
title: "Exploratory Analyses"
author: "Jaime Chen"
date: "2025-03-12"
output: html_document
---

```{r}
# combined_sampling_data %>% group_by(sample_group) %>% select(is_exploratory)
# use subj_test_accuracy_all for test choices
```


# Sampling-Test Interaction
## exploratory choices --> broader extensions?
## adult vs children
### will probably see that exploratory predicts broader extension with adults
### will probably not see this predictor with children --> not effectively using sampling yet?
##### --> age effect?


# correctness by exploratory?

# hit vs FA


# did participants limit test choices based on best extension confirmed/discovered by sampling
## adult vs children
### probably yes with adults
### probably no with kids --> age effect?


# d' by age (5 - 8yrs, adults)

```{r}
age_list = as.character(kid_participant_info$age_group)

subj_test_dprime_avg_training <- subj_test_accuracy_all %>% 
  group_by(sample_group, participant) %>%
  summarize(dprime_t = mean(dprime_training))
subj_test_dprime_avg_training_children <- subj_test_dprime_avg_training %>%
  filter(sample_group == "children") %>% 
  mutate(child_age = age_list)
subj_test_dprime_avg_training_adult <- subj_test_dprime_avg_training %>% 
  filter(sample_group == "adults") %>% mutate(child_age = "adult")
subj_test_dprime_avg_training_clean <- rbind(subj_test_dprime_avg_training_children, subj_test_dprime_avg_training_adult)

# plot here
```

```{r}
subj_test_dprime_avg_label <- subj_test_accuracy_all %>% 
  group_by(sample_group, participant) %>% 
  summarize(dprime_l = mean(dprime_label))
```

