---
title: "Exploratory Analyses"
author: "Jaime Chen"
date: "2025-03-12"
output: html_document
---

# d' (training and learning) by age group (5-, 6-, 7-, 8-yos, and adults)

```{r}
age_list = as.character(kid_participant_info$age_group)
age_cont = kid_participant_info$age_mos / 12

subj_test_dprime_avg_training <- subj_test_accuracy_all %>% 
  group_by(participant, sample_group) %>%
  summarize(dprime_t = mean(dprime_training)) %>% ungroup()

subj_test_dprime_avg_label <- subj_test_accuracy_all %>% 
  group_by(participant, sample_group) %>% 
  summarize(dprime_l = mean(dprime_label)) %>% ungroup()

subj_test_dprime_avg <- subj_test_dprime_avg_training %>% mutate(dprime_l = subj_test_dprime_avg_label$dprime_l)

subj_test_dprime_avg_children <- subj_test_dprime_avg %>%
  filter(sample_group == "children") %>% 
  mutate(age_group = age_list) %>% 
  mutate(age = age_cont)
subj_test_dprime_avg_adult <- subj_test_dprime_avg %>% 
  filter(sample_group == "adults") %>% 
  mutate(age_group = "adult") %>% 
  mutate(age = NA)
subj_test_dprime_avg_clean <- rbind(subj_test_dprime_avg_children, subj_test_dprime_avg_adult)


# plotting d' by age group

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_t, x=age_group)) + geom_violin(draw_quantiles = c(0.5), aes(color=age_group, alpha = 0.1)) + geom_jitter(aes(color = age_group, stroke = 0), size = 2) + theme(legend.position="none")

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_l, x=age_group)) + geom_violin(draw_quantiles = c(0.5), aes(color=age_group, alpha = 0.1)) + geom_jitter(aes(color = age_group, stroke = 0), size = 2) + theme(legend.position="none")

# plotting d' by continuous age

lm_t <- lm(dprime_t ~ age, data = subj_test_dprime_avg_clean)
lm_l <- lm(dprime_l ~ age, data = subj_test_dprime_avg_clean)

summary(lm_t)
summary(lm_l)

subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_t, x=age)) + geom_point() + geom_smooth(method='lm')
subj_test_dprime_avg_clean %>% ggplot(aes(y=dprime_l, x=age)) + geom_point() + geom_smooth(method='lm')


```


# Sampling-Test Interaction
## Exploration-Test
### Do exploratory choices lead to broader extensions in children and adults?

```{r}
exploratory <- combined_sampling_data %>% 
  select(sample_group, participant, trial_counter, is_exploratory) %>%
  sort_by(combined_sampling_data$sample_group, combined_sampling_data$participant) %>%
  mutate(is_exploratory = as.character(is_exploratory)) %>% mutate(is_exploratory_yn = case_when(
    is_exploratory == 1 ~ "explored",
    is_exploratory == 0 ~ "did not explore",
    TRUE ~ is_exploratory
  ))

fa_rate <- subj_test_accuracy_all %>% 
  ungroup() %>% 
  select(sample_group, participant, false_alarm_rate_training_adj, false_alarm_rate_label_adj) %>%
  sort_by(subj_test_accuracy_all$sample_group, subj_test_accuracy_all$participant) %>%
  select(false_alarm_rate_training_adj, false_alarm_rate_label_adj)

choices <- subj_test_accuracy %>% ungroup() %>% select(total_choices, ground_truth_correct_choices, ground_truth_incorrect_choices, training_consistent_choices, training_inconsistent_choices) %>% mutate(training_inconsistent_prop = training_inconsistent_choices/total_choices)

exploratory_interact <- cbind(exploratory, fa_rate, choices)


# adjusted FA rate based on exploration during sampling for each round

exploratory_interact %>% ggplot(aes(x = is_exploratory_yn, y = false_alarm_rate_training_adj)) + geom_violin() + geom_jitter(aes(color = is_exploratory_yn), size = 0.75, alpha = 0.5) + facet_wrap(~ sample_group) + theme(legend.position="none")

exploratory_interact %>% ggplot(aes(x = is_exploratory_yn, y = false_alarm_rate_label_adj)) + geom_violin() + facet_wrap(~ sample_group)


# total choices made based off of explored/didn't explore during sampling for each round

exploratory_interact_total_choice_counts <- exploratory_interact %>% 
  ungroup() %>% 
  group_by(sample_group, is_exploratory_yn, total_choices) %>%
  count() %>% 
  pivot_wider(names_from = total_choices, values_from = n)


exploratory_interact_sums <- exploratory_interact %>% 
  ungroup() %>% 
  group_by(sample_group, is_exploratory_yn, total_choices) %>%
  count() %>% 
  ungroup(total_choices) %>% 
  summarize(sum = sum(n))

exploratory_interact_summarized <- merge(exploratory_interact_total_choice_counts, exploratory_interact_sums) %>% pivot_longer(cols = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12"), names_to = "total_choices", values_to = "count") %>% mutate(proportion = count/sum) %>% select(sample_group, is_exploratory_yn, total_choices, count, proportion) %>% mutate(total_choices = as.integer(total_choices)) %>% mutate(sample_group = case_when(
  sample_group == "adults" ~ "Adults",
  sample_group == "children" ~ "Children",
  TRUE ~ sample_group
))

exploratory_interact_means <- exploratory_interact_summarized %>% ungroup() %>% group_by(sample_group, is_exploratory_yn) %>% summarize(mean = sum(proportion*total_choices, na.rm = TRUE))
  
exploratory_interact_summarized %>% 
  ggplot(aes(x = total_choices, y = proportion, fill = interaction(sample_group, is_exploratory_yn, sep=':'))) + 
  facet_wrap(~ sample_group) + 
  geom_col(position = "dodge") + 
  scale_color_manual(
    values = c("Adults:explored" = "#F8766D", 
               "Adults:did not explore" = "#ffa7a1",
               "Children:explored" = "#00BFC4",
               "Children:did not explore" = "#73DEDE")) +
  scale_fill_manual(
    name = "Explore Status",
    values = c("Adults:explored" = "#F8766D", 
               "Adults:did not explore" = "#ffa7a1",
               "Children:explored" = "#00BFC4",
               "Children:did not explore" = "#73DEDE"),
    breaks = c("Adults:did not explore",
               "Adults:explored",
               "Children:did not explore",
               "Children:explored"),
    labels = c("Adults:explored" = "Explored", 
               "Adults:did not explore" = "Did not explore", 
               "Children:explored" = "Explored", 
               "Children:did not explore" = "Did not explore")) +
  theme(legend.position = c(0.63, 0.863), 
        legend.key.spacing.x = unit(165, "pt"), 
        legend.key.spacing.y = unit(3, "pt"), 
        legend.key = element_rect(fill = "white"),
        legend.title=element_blank(),
        legend.background=element_blank()
        ) +
  guides(fill = guide_legend(title.position = "top", ncol = 2), color = "none") +
  xlab("Number of Test Images Chosen during a Round") + 
  ylab("Proportion of Rounds") +
  ylim(0, 0.5) + 
  scale_x_discrete(limits=c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12"))


# add density curve
```





## Sampling Consistency of Test Choices
### Did participants limit test choices based on best extension confirmed/discovered by sampling and training (match b/w samp and test)?

#### Children

```{r}
kid_sampling_samptestint <- kid_sampling_data %>% select(participant, age_group, age_years, age_mos, exclude_participant, trial_counter, round, number_training_images, current_category_kind, current_category_training_level, current_hypernym_category_kind, sampled_image, sampled_imagelabel, sampled_category_kind, sampled_category_level, sampling_choice_type, sampled_label) %>% group_by(participant, trial_counter) %>% 
  mutate(current_category_training_level = case_when(
    number_training_images == 1 ~ "sub",
    number_training_images == 3 & current_category_training_level == "narrow" ~ "sub",
    number_training_images == 3 & current_category_training_level == "intermediate" ~ "bas",
    number_training_images == 3 & current_category_training_level == "broad" ~ "sup",
    TRUE ~ current_category_training_level
  ))

kid_sampling_samptestint <- kid_sampling_samptestint %>% 
  mutate(sampling_consistent_cat = case_when(
    current_category_kind == sampled_category_kind ~ substr(current_category_kind, start=1, stop=3),
    current_category_kind != sampled_category_kind & "not" == substr(sampled_label, start=1, stop=3) ~ substr(current_category_kind, start=1, stop=3),
    current_category_kind != sampled_category_kind & "not" != substr(sampled_label, start=1, stop=3) ~ paste(substr(current_category_kind, start=1, stop=3), substr(sampled_category_kind, start=1, stop=3)),
    TRUE ~ current_category_kind
  )) %>% 
  mutate(current_category_training_level_num = case_when(
    current_category_training_level == "sub" ~ 1,
    current_category_training_level == "bas" ~ 2,
    current_category_training_level == "sup" ~ 3,
    TRUE ~ 0
  )) %>% 
  mutate(sampled_category_level_num = case_when(
    sampled_category_level == "sub" ~ 1,
    sampled_category_level == "bas" ~ 2,
    current_category_kind == sampled_category_kind & sampled_category_level == "sup" ~ 3,
    current_category_kind != sampled_category_kind ~ 4,
    TRUE ~ 0
  )) %>% 
  mutate(sampling_consistent_level = case_when(
    current_category_kind != sampled_category_kind & "not" != substr(sampled_label, start=1, stop=3) ~ "hyp",
    "not" != substr(sampled_label, start=1, stop=3) & sampled_category_level_num >= current_category_training_level_num ~ sampled_category_level,
    "not" != substr(sampled_label, start=1, stop=3) & sampled_category_level_num < current_category_training_level_num ~ current_category_training_level,
    "not" == substr(sampled_label, start=1, stop=3) ~ current_category_training_level,
    TRUE ~ NA
  ))

kid_test_samptestint <- kid_test_array_options_clean %>% select(participant, trial_counter, round, test_image, is_chosen)

kid_samptestint <- merge(kid_test_samptestint, kid_sampling_samptestint)


hyp_consistent = c("sub", "bas", "sup", "hyp")
sup_consistent = c("sub", "bas", "sup")
bas_consistent = c("sub", "bas")
sub_consistent = c("sub")


# how many sampling+training consistent choices they made (e.g, sampling_consistent is 1 and is_chosen is 1)
# how many sampling+training inconsistent choices they made (e.g, sampling_consistent is 0 but is_chosen is 1)
# how many sampling+training consistent choices they missed (e.g, sampling_consistent is 1 but is_chosen is 0)

kid_samptestint <- kid_samptestint %>% rowwise() %>% 
  mutate(test_image_level = case_when(
    grepl("sub", test_image) ~ "sub",
    grepl("bas", test_image) ~ "bas",
    grepl("sup", test_image) ~ "sup",
    TRUE ~ test_image
  )) %>%
  mutate(test_image_cat = case_when(
    grepl((substr(current_hypernym_category_kind, start=1, stop=3)), test_image) ~ "out_hyp",
    grepl((substr(current_category_kind, start=1, stop=3)), test_image) ~ "in",
    .default = "out"
  ))

kid_samptestint <- kid_samptestint %>%
  mutate(sampling_consistent = case_when(
    sampling_consistent_level == "sub" & test_image_cat == "in" & test_image_level == "sub" ~ 1,
    sampling_consistent_level == "bas" & test_image_cat == "in" & test_image_level == "bas" ~ 1,
    sampling_consistent_level == "bas" & test_image_level == "sub" ~ 1,
    sampling_consistent_level == "sup" & test_image_cat == "in" ~ 1,
    sampling_consistent_level == "hyp" & test_image_cat == "in" ~ 1,
    sampling_consistent_level == "hyp" & test_image_cat == "out_hyp" ~ 1,
    .default = 0
  ))

kid_sample_choice_consistency <- kid_samptestint %>% ungroup() %>% group_by(participant, trial_counter) %>% select(participant, age_group, age_years, age_mos, trial_counter, round, number_training_images, current_category_training_level, sampling_consistent_level, is_chosen, sampling_consistent, current_category_training_level_num, sampled_category_level_num) %>% 
  mutate(choice_type = case_when(
    is_chosen == 1 & sampling_consistent == 1 ~ "hit",
    is_chosen == 1 & sampling_consistent == 0 ~ "false_alarm",
    is_chosen == 0 & sampling_consistent == 1 ~ "miss",
    is_chosen == 0 ~ "correct_reject",
    .default = NA
  ))

kid_choice_type_count <- kid_sample_choice_consistency %>% 
  ungroup() %>% 
  group_by(participant) %>% 
  count(choice_type)

kid_choice_type_count %>% ggplot(aes(x = choice_type, y = n)) + geom_violin()

kid_choice_type_rate <- kid_choice_type_count %>% 
  pivot_wider(names_from = choice_type, values_from = n)

kid_choice_type_rate[is.na(kid_choice_type_rate)] <- 0

kid_participant_ages <- kid_sampling_data %>% select(participant, age_group, age_years, age_mos) %>% unique() %>% mutate(group = case_when(
    TRUE ~ "1_child"
  ))

kid_choice_type_rate <- kid_choice_type_rate %>% mutate(hit_rate = hit/(hit+miss)) %>% mutate(fa_rate = false_alarm/(false_alarm+correct_reject)) %>% ungroup() %>% mutate(miss_rate = miss/(hit+miss)) %>% merge(kid_participant_ages)

kid_choice_type_rate %>% ggplot(aes(x=age_years, y=hit_rate)) + geom_point()
kid_choice_type_rate %>% ggplot(aes(x=age_years, y=fa_rate)) + geom_point()
kid_choice_type_rate %>% ggplot(aes(x=age_years, y=miss_rate)) + geom_point()

```

#### Adults

```{r}
adult_hypernym_data <- adult_d %>% select(participant, current_category_kind, current_hypernym_category_kind) %>% unique() %>% na.omit()

adult_sampling_data <- merge(adult_sampling_data, adult_hypernym_data)

adult_sampling_samptestint <- adult_sampling_data %>% select(participant, exclude_participant, trial_counter, round, number_training_images, current_category_kind, current_category_training_level, current_hypernym_category_kind, sampled_image, sampled_imagelabel, sampled_category_kind, sampled_category_level, sampling_choice_type, sampled_label) %>% group_by(participant, trial_counter) %>% 
  mutate(current_category_training_level = case_when(
    number_training_images == 1 ~ "sub",
    number_training_images == 3 & current_category_training_level == "narrow" ~ "sub",
    number_training_images == 3 & current_category_training_level == "intermediate" ~ "bas",
    number_training_images == 3 & current_category_training_level == "broad" ~ "sup",
    TRUE ~ current_category_training_level
  ))

adult_sampling_samptestint <- adult_sampling_samptestint %>% 
  mutate(sampling_consistent_cat = case_when(
    current_category_kind == sampled_category_kind ~ substr(current_category_kind, start=1, stop=3),
    current_category_kind != sampled_category_kind & "not" == substr(sampled_label, start=1, stop=3) ~ substr(current_category_kind, start=1, stop=3),
    current_category_kind != sampled_category_kind & "not" != substr(sampled_label, start=1, stop=3) ~ paste(substr(current_category_kind, start=1, stop=3), substr(sampled_category_kind, start=1, stop=3)),
    TRUE ~ current_category_kind
  )) %>% 
  mutate(current_category_training_level_num = case_when(
    current_category_training_level == "sub" ~ 1,
    current_category_training_level == "bas" ~ 2,
    current_category_training_level == "sup" ~ 3,
    TRUE ~ 0
  )) %>% 
  mutate(sampled_category_level_num = case_when(
    sampled_category_level == "sub" ~ 1,
    sampled_category_level == "bas" ~ 2,
    current_category_kind == sampled_category_kind & sampled_category_level == "sup" ~ 3,
    current_category_kind != sampled_category_kind ~ 4,
    TRUE ~ 0
  )) %>% 
  mutate(sampling_consistent_level = case_when(
    current_category_kind != sampled_category_kind & "not" != substr(sampled_label, start=1, stop=3) ~ "hyp",
    "not" != substr(sampled_label, start=1, stop=3) & sampled_category_level_num >= current_category_training_level_num ~ sampled_category_level,
    "not" != substr(sampled_label, start=1, stop=3) & sampled_category_level_num < current_category_training_level_num ~ current_category_training_level,
    "not" == substr(sampled_label, start=1, stop=3) ~ current_category_training_level,
    TRUE ~ NA
  ))
# what about when sampling gives "not a ___" but they sampled 2 or 3 levels up (e.g., sub training, sup/hyp sampling)

adult_test_samptestint <- adult_test_array_options_clean %>% select(participant, trial_index, round, test_image, is_chosen) %>% mutate(trial_counter = (trial_index-1)/7) %>% select(participant, trial_counter, round, test_image, is_chosen)

adult_samptestint <- merge(adult_test_samptestint, adult_sampling_samptestint)

hyp_consistent = c("sub", "bas", "sup", "hyp")
sup_consistent = c("sub", "bas", "sup")
bas_consistent = c("sub", "bas")
sub_consistent = c("sub")

# how many sampling+training consistent choices they made (e.g, sampling_consistent is 1 and is_chosen is 1)
# how many sampling+training inconsistent choices they made (e.g, sampling_consistent is 0 but is_chosen is 1)
# how many sampling+training consistent choices they missed (e.g, sampling_consistent is 1 but is_chosen is 0)

adult_samptestint <- adult_samptestint %>% rowwise() %>% 
  mutate(test_image_level = case_when(
    grepl("sub", test_image) ~ "sub",
    grepl("bas", test_image) ~ "bas",
    grepl("sup", test_image) ~ "sup",
    TRUE ~ test_image
  )) %>%
  mutate(test_image_cat = case_when(
    grepl((substr(current_hypernym_category_kind, start=1, stop=3)), test_image) ~ "out_hyp",
    grepl((substr(current_category_kind, start=1, stop=3)), test_image) ~ "in",
    .default = "out"
  ))

adult_samptestint <- adult_samptestint %>%
  mutate(sampling_consistent = case_when(
    sampling_consistent_level == "sub" & test_image_cat == "in" & test_image_level == "sub" ~ 1,
    sampling_consistent_level == "bas" & test_image_cat == "in" & test_image_level == "bas" ~ 1,
    sampling_consistent_level == "bas" & test_image_level == "sub" ~ 1,
    sampling_consistent_level == "sup" & test_image_cat == "in" ~ 1,
    sampling_consistent_level == "hyp" & test_image_cat == "in" ~ 1,
    sampling_consistent_level == "hyp" & test_image_cat == "out_hyp" ~ 1,
    .default = 0
  ))


adult_sample_choice_consistency <- adult_samptestint %>% ungroup() %>% group_by(participant, trial_counter) %>% select(participant, trial_counter, round, number_training_images, current_category_training_level, sampling_consistent_level, is_chosen, sampling_consistent, current_category_training_level_num, sampled_category_level_num) %>% 
  mutate(choice_type = case_when(
    is_chosen == 1 & sampling_consistent == 1 ~ "hit",
    is_chosen == 1 & sampling_consistent == 0 ~ "false_alarm",
    is_chosen == 0 & sampling_consistent == 1 ~ "miss",
    is_chosen == 0 ~ "correct_reject",
    .default = NA
  ))

adult_choice_type_count <- adult_sample_choice_consistency %>% 
  ungroup() %>% 
  group_by(participant) %>% 
  count(choice_type)

adult_choice_type_count %>% ggplot(aes(x = choice_type, y = n)) + geom_violin()

adult_choice_type_rate <- adult_choice_type_count %>% 
  pivot_wider(names_from = choice_type, values_from = n)

adult_choice_type_rate[is.na(adult_choice_type_rate)] <- 0

adult_participant_ages <- adult_sampling_data %>% select(participant) %>% unique() %>% 
  mutate(age_years = case_when(
    TRUE ~ 25
  )) %>% 
  mutate(group = case_when(
    TRUE ~ "2_adult"
  ))

adult_choice_type_rate <- adult_choice_type_rate %>% mutate(hit_rate = hit/(hit+miss)) %>% mutate(fa_rate = false_alarm/(false_alarm+correct_reject)) %>% ungroup() %>% mutate(miss_rate = miss/(hit+miss)) %>% merge(adult_participant_ages)
```

#### Plotting Children and Adults together

```{r}
kid_choice_type_rate_2 <- kid_choice_type_rate %>% select(-age_group, -age_mos)

samptestint_choice_type_rate <- rbind(adult_choice_type_rate, kid_choice_type_rate_2)

plot1 <- samptestint_choice_type_rate %>% filter(group == "1_child") %>% ggplot(aes(x = age_years, y = hit_rate)) + geom_point() + scale_y_continuous(limits=c(-0.01, 1.01)) + geom_smooth(method = "lm")

plot2 <- samptestint_choice_type_rate %>% filter(group == "2_adult") %>% ggplot(aes(x = group, y = hit_rate)) + geom_jitter() + scale_y_continuous(limits=c(-0.01, 1.01))

plot3 <- samptestint_choice_type_rate %>% filter(group == "1_child") %>% ggplot(aes(x = age_years, y = fa_rate)) + geom_point() + scale_y_continuous(limits=c(-0.01, 1.01)) + geom_smooth(method = "lm")

plot4 <- samptestint_choice_type_rate %>% filter(group == "2_adult") %>% ggplot(aes(x = group, y = fa_rate)) + geom_jitter() + scale_y_continuous(limits=c(-0.01, 1.01))

plot5 <- samptestint_choice_type_rate %>% filter(group == "1_child") %>% ggplot(aes(x = age_years, y = miss_rate)) + geom_point() + scale_y_continuous(limits=c(-0.01, 1.01)) + geom_smooth(method = "lm")

plot6 <- samptestint_choice_type_rate %>% filter(group == "2_adult") %>% ggplot(aes(x = group, y = miss_rate)) + geom_jitter() + scale_y_continuous(limits=c(-0.01, 1.01))

(plot1+plot2)
(plot3+plot4)
(plot5+plot6)
```

## Exploration Consistent Test Choices?
### Did exploration (and associated sampling feedback) actually have an effect on how participants extended the novel word? 

#### Separating participants by explored/didn't explore 

```{r}
exp_adult_samptestint <- adult_samptestint %>% mutate(explored_yn = case_when(
  sampled_category_level_num > current_category_training_level_num ~ "explored",
  sampled_category_level_num <= current_category_training_level_num ~ "did not explore",
  TRUE ~ NA
)) %>% 
  mutate(samp_feedback_type = case_when(
    current_category_training_level == sampling_consistent_level & sampling_choice_type == "explore" ~ "negative",
    current_category_training_level != sampling_consistent_level & sampling_choice_type == "explore" ~ "positive",
    sampling_choice_type == "confirm" ~ "confirming",
    TRUE ~ NA
  )) %>% 
  ungroup() %>% group_by(participant, trial_counter)

exp_kid_samptestint <- kid_samptestint %>% mutate(explored_yn = case_when(
  sampled_category_level_num > current_category_training_level_num ~ "explored",
  sampled_category_level_num <= current_category_training_level_num ~ "did not explore",
  TRUE ~ NA
)) %>% 
  mutate(samp_feedback_type = case_when(
    current_category_training_level == sampling_consistent_level & sampling_choice_type == "explore" ~ "negative",
    current_category_training_level != sampling_consistent_level & sampling_choice_type == "explore" ~ "positive",
    sampling_choice_type == "confirm" ~ "confirming",
    TRUE ~ NA
  )) %>% 
  ungroup() %>% group_by(participant, trial_counter)


# Looking at proportion of sampling inconsistent choices made (e.g., extending words broader than what was confirmed by sampling and/or exploring)

exp_adult_samptestint_sampinconsistent <- exp_adult_samptestint %>% filter(is_chosen == 1) %>% summarize(prop_sampinconsistent_choices = sum(is_chosen - sampling_consistent)/sum(is_chosen), explored_yn, samp_feedback_type) %>% unique() %>% mutate(samp_group = "adult")

exp_kid_samptestint_sampinconsistent <- exp_kid_samptestint %>% filter(is_chosen == 1) %>% summarize(prop_sampinconsistent_choices = sum(is_chosen - sampling_consistent)/sum(is_chosen), explored_yn, samp_feedback_type) %>% unique() %>% mutate(samp_group = "child")

exp_sampinconsistent <- rbind(exp_adult_samptestint_sampinconsistent, exp_kid_samptestint_sampinconsistent)

exp_sampinconsistent %>% ggplot(aes(x = samp_group, y = prop_sampinconsistent_choices, color = samp_group)) + geom_violin() + geom_jitter(alpha = 0.2) + facet_grid(explored_yn~samp_feedback_type)


## Looking at proportion of sampling consistent choices missed

# exp_adult_samptestint_missed <- exp_adult_samptestint %>% filter(sampling_consistent == 1) %>% mutate(is_not_chosen = -(is_chosen - 1)) %>% summarize(prop_sampconsistent_missed = sum(is_not_chosen)/sum(sampling_consistent), explored_yn, samp_feedback_type) %>% unique() %>% mutate(samp_group = "adult")
# 
# 
# exp_kid_samptestint_missed <- exp_kid_samptestint %>% filter(sampling_consistent == 1) %>% mutate(is_not_chosen = -(is_chosen - 1)) %>% summarize(prop_sampconsistent_missed = sum(is_not_chosen)/sum(sampling_consistent), explored_yn, samp_feedback_type) %>% unique() %>% mutate(samp_group = "child")

# 
# exp_missed <- rbind(exp_adult_samptestint_missed, exp_kid_samptestint_missed)
# 
# exp_missed %>% ggplot(aes(x = samp_group, y = prop_sampconsistent_missed, color = samp_group)) + geom_violin() + geom_jitter(alpha = 0.2) + facet_grid(explored_yn~samp_feedback_type)

```

# separating explorers by how many levels up they explored in sampling

```{r}

exp_adult <- adult_samptestint %>% mutate(test_image_level_num = case_when(
    test_image_level == "sub" & test_image_cat == "in" ~ 1,
    test_image_level == "bas" & test_image_cat == "in" ~ 2,
    test_image_level == "sup" & test_image_cat == "in" ~ 3,
    test_image_cat == "out_hyp" ~ 4,
    test_image_cat == "out" ~ 5,
    TRUE ~ 0
  )) %>% filter(is_chosen == 1) %>% select(participant, trial_counter, number_training_images, sampling_choice_type, current_category_training_level_num, sampled_category_level_num, test_image_level_num, sampling_consistent)

exp_kid <- kid_samptestint %>% mutate(test_image_level_num = case_when(
    test_image_level == "sub" & test_image_cat == "in" ~ 1,
    test_image_level == "bas" & test_image_cat == "in" ~ 2,
    test_image_level == "sup" & test_image_cat == "in" ~ 3,
    test_image_cat == "out_hyp" ~ 4,
    test_image_cat == "out" ~ 5,
    TRUE ~ 0
  )) %>% filter(is_chosen == 1) %>% select(participant, trial_counter, number_training_images, sampling_choice_type, current_category_training_level_num, sampled_category_level_num, test_image_level_num, sampling_consistent)

exp_all <- rbind(exp_adult, exp_kid) %>% rowwise() %>% mutate(samp_train_level_diff = sampled_category_level_num - current_category_training_level_num) %>% mutate(test_image_level = case_when(
  test_image_level_num > sampled_category_level_num & sampling_choice_type == "explore" ~ "above_exp_sampling",
  test_image_level_num == sampled_category_level_num & sampling_choice_type == "explore" ~ "same_exp_sampling",
  test_image_level_num > sampled_category_level_num & sampling_choice_type == "confirm" ~ "above_conf_sampling",
  test_image_level_num <= current_category_training_level_num ~ "same_or_below_training",
  test_image_level_num < sampled_category_level_num & test_image_level_num > current_category_training_level_num ~ "below_sampling_above_training"
))

exp_all_count <- exp_all %>% group_by(participant, trial_counter, number_training_images, samp_train_level_diff) %>% count(test_image_level) %>% pivot_wider(names_from = test_image_level, values_from = n)

exp_feedback <- exp_sampinconsistent %>% select(participant, samp_group, trial_counter, samp_feedback_type)

exp_all_feedback <- merge(exp_feedback, exp_all_count)


# summarizing counts of test choice types based on sample group and feedback type

feedback_summarized <- exp_all_feedback %>% 
  ungroup() %>% 
  group_by(samp_group, samp_feedback_type) %>%
  summarize(
    a_above_exp_sampling = sum(above_exp_sampling, na.rm = TRUE), 
    b_same_exp_sampling = sum(same_exp_sampling, na.rm = TRUE), 
    a_above_conf_sampling = sum(above_conf_sampling, na.rm = TRUE), 
    d_same_or_below_training = sum(same_or_below_training, na.rm = TRUE), 
    c_below_sampling_above_training = sum(below_sampling_above_training, na.rm = TRUE))

confirm_feedback_summarized <- feedback_summarized %>% filter(samp_feedback_type == "confirming") %>%
  mutate(samp_group = case_when(
    samp_group == "adult" ~ "Adults",
    samp_group == "child" ~ "Children",
    TRUE ~ samp_group
    )) %>% 
  select(samp_group, samp_feedback_type, d_same_or_below_training, a_above_conf_sampling) %>%
  pivot_longer(cols = c(d_same_or_below_training, a_above_conf_sampling), names_to = "test_choice_type") %>% ungroup() %>% group_by(samp_group, samp_feedback_type) %>% summarize(test_choice_type, proportion = value/sum(value))

explore_feedback_summarized <- feedback_summarized %>% 
  filter(samp_feedback_type == "positive" | samp_feedback_type == "negative") %>% 
   mutate(samp_group = case_when(
    samp_group == "adult" ~ "Adults",
    samp_group == "child" ~ "Children",
    TRUE ~ samp_group
    )) %>% 
  mutate(samp_feedback_type = case_when(
    samp_feedback_type == "positive" ~ "Positive Feedback",
    samp_feedback_type == "negative" ~ "Negative Feedback",
    TRUE ~ samp_feedback_type
  )) %>% 
  select(samp_group, samp_feedback_type, d_same_or_below_training, c_below_sampling_above_training, b_same_exp_sampling, a_above_exp_sampling) %>% 
  pivot_longer(cols = c(d_same_or_below_training, c_below_sampling_above_training, b_same_exp_sampling, a_above_exp_sampling), names_to = "test_choice_type") %>% ungroup() %>% group_by(samp_group, samp_feedback_type) %>% summarize(test_choice_type, proportion = value/sum(value))

conf_labs = c(">S", "\u2264T")
exp_labs = c(">S", "=S", "<S,>T", "\u2264T")

```

```{r}

# Plotting

plot1 <- confirm_feedback_summarized %>% ggplot(aes(x = test_choice_type, y = proportion, fill = samp_group)) + geom_col() + facet_wrap(~samp_group) + labs(title = "Confirmatory Sampling", ) + theme(legend.position="none", plot.title = element_text(hjust = 0.5)) + scale_x_discrete(labels = conf_labs) + ylim(0, 0.8) + xlab("Category Level of Test Extensions") + ylab("Proportion of Test Extensions")

plot2 <- explore_feedback_summarized %>% group_by(samp_feedback_type) %>% 
  ggplot(aes(x = test_choice_type, 
             y = proportion, 
             fill = samp_group, 
             pattern = samp_feedback_type, 
             pattern_color = samp_feedback_type,
             pattern_fill = samp_feedback_type,
             pattern_spacing = 0.02,
             pattern_size = 0.3)) + 
  labs(title = "Exploratory Sampling") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_col_pattern(
    position = "dodge", 
    show.legend = TRUE,
    pattern_size = 0.3,
    pattern_spacing = 0.02
    ) + 
  scale_pattern_manual(
    name = "Feedback Type",
    values = c(
      "Negative Feedback" = "stripe",
      "Positive Feedback" = "circle"
    )
  ) +
  scale_pattern_color_manual(
    name = "Feedback Type",
    values = c(
      "Negative Feedback" = "black",
      "Positive Feedback" = "white"
    ),
    guide = guide_legend(override.aes = list(fill = "#999"))
  ) +
  scale_pattern_fill_manual(
    name = "Feedback Type",
    values = c(
      "Negative Feedback" = "black",
      "Positive Feedback" = "white"
    )
  ) +
  scale_pattern_size_manual(
    name = "Feedback Type",
    values = 0.3
  ) +
  scale_pattern_spacing_manual(
    name = "Feedback Type",
    values = 0.02
  ) +
  facet_wrap(~samp_group) + 
  scale_x_discrete(labels = exp_labs) + 
  xlab("Category Level of Test Extensions") + 
  ylab("Proportion of Test Extensions") + 
  ylim(0, 0.8) +
  guides(fill = "none") +
  theme(legend.position = c(0.71, 0.82), legend.key.size = unit(0.4, 'cm'))

patch <- ((plot1 + theme(plot.margin = unit(c(0,10,0,0), "pt"))) + (plot2 & ylab(NULL)) & xlab(NULL)) + plot_layout(widths = c(2, 5))

patch2 <- wrap_elements(panel = patch) +
  labs(tag = "Category Level of Test Extensions") +
  theme(
    plot.tag = element_text(size = rel(1), vjust = 3),
    plot.tag.position = "bottom",
  )


abbreviation <- c(">S", "=S", "<S,>T", "\u2264T")
meaning <- c("broader than sampling level", "same level as sampling level", "narrower than sampling level, broader than training level", "narrower or equal to training level")


key <- data.frame(abbreviation, meaning)
key_legend <- tableGrob(key, cols = NULL, rows = NULL, theme = ttheme_default(base_size = 10, padding = unit(c(1.5, 1.5), "mm")))

patch2 / key_legend + plot_layout(heights = c(7, 1))

```


```{r}
# [continued from above] separating feedback and summaries by sampling level (how many levels up/down was the sampling choice compared to training)

feedback_summarized_by_level <- exp_all_feedback %>% 
  ungroup() %>% 
  group_by(samp_group, samp_feedback_type, samp_train_level_diff) %>%
  summarize(
    above_exp_sampling = sum(above_exp_sampling, na.rm = TRUE), 
    same_exp_sampling = sum(same_exp_sampling, na.rm = TRUE), 
    above_conf_sampling = sum(above_conf_sampling, na.rm = TRUE), 
    same_or_below_training = sum(same_or_below_training, na.rm = TRUE), 
    below_sampling_above_training = sum(below_sampling_above_training, na.rm = TRUE))

confirm_feedback_summarized_by_level <- feedback_summarized_by_level %>% filter(samp_feedback_type == "confirming") %>% select(samp_group, samp_feedback_type, samp_train_level_diff, same_or_below_training, above_conf_sampling)

explore_feedback_summarized_by_level <- feedback_summarized_by_level %>% filter(samp_feedback_type == "positive" | samp_feedback_type == "negative") %>% select(samp_group, samp_feedback_type, samp_train_level_diff, same_or_below_training, below_sampling_above_training, same_exp_sampling, above_exp_sampling)
```




# Play with participant-provided hypotheses

```{r}
hypothesis_adult <- read_csv("hypothesis_coding_prelim_adults.csv") %>% mutate(samp_group = "adult")
hypothesis_kid <- read_csv("hypothesis_coding_prelim_children.csv") %>% mutate(samp_group = "child")

hypothesis_level_adult <- hypothesis_adult %>% select(participant, samp_group, trial_counter, hypothesis_level)

hypothesis_level_kid <- hypothesis_kid %>% select(participant, samp_group, trial_counter, hypothesis_level)

hypothesis_level = rbind(hypothesis_level_adult, hypothesis_level_kid)

# filter out unsure/un-codable things (i.e., not sub, bas, sup, hyp)

hypothesis_level <- hypothesis_level %>% filter(hypothesis_level == "sub" | hypothesis_level == "bas" | hypothesis_level == "sup" | hypothesis_level == "hyp")


# seeing if hypotheses are sampling consistent, narrower, or broader

hypothesis_level <- hypothesis_level %>% mutate(hypothesis_level_num = case_when(
  hypothesis_level == "sub" ~ 1,
  hypothesis_level == "bas" ~ 2,
  hypothesis_level == "sup" ~ 3,
  hypothesis_level == "hyp" ~ 4,
  TRUE ~ NA
))

kid_sampling_samptestint_hypothesisanalysis <- kid_sampling_samptestint %>% select(participant, trial_counter, number_training_images, sampling_consistent_level) %>% mutate(samp_cons_level_num = case_when(
  sampling_consistent_level == "sub" ~ 1,
  sampling_consistent_level == "bas" ~ 2,
  sampling_consistent_level == "sup" ~ 3,
  sampling_consistent_level == "hyp" ~ 4,
  TRUE ~ NA
)) %>% mutate(samp_group = "child")

sampling_vs_hypothesis <- adult_sampling_samptestint %>% select(participant, trial_counter, number_training_images, sampling_consistent_level) %>% mutate(samp_cons_level_num = case_when(
  sampling_consistent_level == "sub" ~ 1,
  sampling_consistent_level == "bas" ~ 2,
  sampling_consistent_level == "sup" ~ 3,
  sampling_consistent_level == "hyp" ~ 4,
  TRUE ~ NA
)) %>% mutate(samp_group = "adult") %>%
  rbind(kid_sampling_samptestint_hypothesisanalysis) %>% 
  merge(hypothesis_level)

sampling_vs_hypothesis <- sampling_vs_hypothesis %>% 
  mutate(hypothesis_sampling_agreement = case_when(
    samp_cons_level_num == hypothesis_level_num ~ "agree",
    samp_cons_level_num < hypothesis_level_num ~ "hypothesis is broader",
    samp_cons_level_num > hypothesis_level_num ~ "hypothesis is narrower",
    TRUE ~ NA
  ))

summarized_sampling_vs_hypothesis <- sampling_vs_hypothesis %>% group_by(samp_group, number_training_images) %>% count(hypothesis_sampling_agreement)

sampling_vs_hypothesis <- sampling_vs_hypothesis %>% group_by(samp_group, number_training_images)

sampling_vs_hypothesis %>% ggplot(aes(x = hypothesis_sampling_agreement, fill = samp_group)) + 
  facet_grid(samp_group~number_training_images, labeller = as_labeller(
               c("1" = "1-Item Condition", "3" = "3-Item Condition", "adult" = "adult", "child" = "child"))) + 
  geom_bar() + coord_flip() + theme(strip.background = element_blank(), strip.placement = "outside") + labs(x = "Hypothesis VS Broadest Confirmed Cat Level", y = "Count")

# look at relationship between alignment of sampling consistency and hypothesis based on number of training images, training level, and age
```

